Writing a reproducible paper with RStudio and Quarto

### 2023-03-03 paper.qmd
adjust link to gdrive folder that contains alle files for download.

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  html: default
  pdf: default
date: 'last-modified'
date-format: "[First version:February  16, 2023<br>This version:] MMMM D, YYYY"
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series on other templates, namely on RMarkdown and pagedown that can be downloaded [here](https://osf.io/k8jhx/) [@Bauer2018-dl] and [here](https://osf.io/q395s) [@Bauer2021-dl]. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s?usp=sharing). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
number-sections: true
execute: 
  echo: false
  warning: false
  message: false
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://posit.co/download/rstudio-desktop/) (important: most recent versions, e.g. RStudio v2022.07) [@R2017; @Rstudio2015].
* ...install the "rmarkdown"-package from CRAN using the code below [@markdown2017].
```{r eval=FALSE, echo=TRUE}
install.packages("rmarkdown")
```
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex] in order to compile PDFs.
```{r eval=FALSE, echo=TRUE}
install.packages('tinytex')
tinytex::install_tinytex()
```
* ...also install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra].
```{r eval=FALSE, echo=TRUE}
install.packages(c("knitr", "kableExtra",
                   "stargazer", "modelsummary", "knitr", "gt"))
```
* ...download the 3 input files we created --- `paper.qmd`, `references.bib` and `data.csv` --- from [this folder](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing). Ignore the other files.
* ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

[Download these files](https://drive.google.com/drive/folders/1rWzj-Bu1EKqkSuE1gaFzduBJhzlThpkw?usp=sharing) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.^[You can always check your working directory in R with `getwd()`.]

>>>>

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  html: default
  pdf: default
date: 'last-modified'
date-format: "[First version:February  16, 2023<br>This version:] MMMM D, YYYY"
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series on other templates, namely on RMarkdown and pagedown that can be downloaded [here](https://osf.io/k8jhx/) [@Bauer2018-dl] and [here](https://osf.io/q395s) [@Bauer2021-dl]. Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
tbl-cap-location: top
number-sections: true
execute: 
  echo: false
  warning: false
  message: false
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://posit.co/download/rstudio-desktop/) (important: most recent versions, e.g. RStudio v2022.07) [@R2017; @Rstudio2015].
* ...install the "rmarkdown"-package from CRAN using the code below [@markdown2017].
```{r eval=FALSE, echo=TRUE}
install.packages("rmarkdown")
```
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex] in order to compile PDFs.
```{r eval=FALSE, echo=TRUE}
install.packages('tinytex')
tinytex::install_tinytex()
```
* ...also install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra].
```{r eval=FALSE, echo=TRUE}
install.packages(c("knitr", "kableExtra",
                   "stargazer", "modelsummary", "knitr", "gt"))
```
* ...download the 3 input files we created --- `paper.qmd`, `references.bib` and `data.csv` --- from [this folder](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s). Ignore the other files.
* ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

[Download these files](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.^[You can always check your working directory in R with `getwd()`.]
